Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2016-01-26 latex/article.tex
ok

In~\cite{DGCI2013}, \comJeremy{authors define a  2D digital curvature estimator $\CurvH{R}$
and a 3D digital mean curvature estimator $\MeanCurvH{R}$  based on the
digital volume estimator $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (area estimator $\AreaC(Y,h)$ in dimension 2):}
%% Redite
%% \Jaco{Given some point $\vx \in \R^d$, the set $Y$ is the digital intersection of $\DigShape$ with the ball of radius $R/h$ and center $\vx/h$.}
%% where $Y$ is the intersection of $\DigShape$ with a ball
%% $\Ball{R/h}{\vx/h}$ with $\MCard(Y)$, the number of digital points of
%% the intersection between a ball $\Ball{R/h}{\vx/h}$ of digital radius
%% $R/h$ and $\DigShape$ (we denote such quantity $\AreaC(Y,h)$ in
%% dimension 2):
%
\begin{Definition}
  %
  Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
  (or $\R^3$ for the 3D mean curvature estimator), \emph{digital curvature
  estimators} are defined for any point $\vx \in \R^2$ (or $\R^3$) as:
  %
  \vspace{-0.05cm}
  %
  \begin{align}
    \forall 0 < h < R,\quad
    &\CurvH{R}(Z,\vx,h) \EqDef \frac{3\pi}{2R}
    - \frac{3\AreaC(\Ball{R/h}{\vx/h} \cap
    {Z}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
    &\MeanCurvH{R}(Z,\vx,h) \EqDef \frac{8}{3R}
    - \frac{4\VolC(\Ball{R/h}{\vx/h} \cap
    Z, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
  \end{align}
  %
  where $\Ball{R/h}{\vx/h}$ is the ball of digital radius $R/h$ centered on
  digital point $(\vx/h) \in Z$.
  %
  % \AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
  % \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
  % \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
  % the number of digital points in the intersection between $\Body{\DSh}{h}$ and
  % the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
  % $h^d$.\todo[inline]{J: Hum... pas top...}
  %
  % Similarly, $\hat{\lambda}_1$
  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
  % matrix of the digital points in the intersection between $Z$ and the ball.
  %
\end{Definition}
%
\comJeremy{Such curvature estimators have multigrid convergence
  properties~\cite{DGCI2013}:} For short, when
the digital object becomes finer and finer, \ie when the digitization
step $h$ tends to zero, the estimated quantity on
$\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to
the \txtblue{ associated one on $\Bd{\Shape}$ in
  $O\left(h^{\frac{1}{3}}\right)$ for convex shapes with at least
  $C^3$-boundary and bounded curvature (setting $R\EqDef
  kh^\frac{1}{3}$ for some $k\in\R$).}
%
%Since our digital estimators are defined on
%digital shapes, in order to compare results with the exact curvature on
%Euclidean shape, we need to match points on boundary of the digital
%shape and points on the border of the Euclidean one.
%
%Setting $R = kh^\frac{1}{3}$ on convex shapes
%with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
%related to the maximal curvature of the shape, they have:
%%
%\begin{align}
%\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
%\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
%&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
%&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
%\end{align}

>>>>

In~\cite{DGCI2013}, \comJeremy{authors define a  2D digital curvature estimator $\CurvH{R}$
and a 3D digital mean curvature estimator $\MeanCurvH{R}$  based on the
digital volume estimator $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (area estimator $\AreaC(Y,h)$ in dimension 2):}
%% Redite
%% \Jaco{Given some point $\vx \in \R^d$, the set $Y$ is the digital intersection of $\DigShape$ with the ball of radius $R/h$ and center $\vx/h$.}
%% where $Y$ is the intersection of $\DigShape$ with a ball
%% $\Ball{R/h}{\vx/h}$ with $\MCard(Y)$, the number of digital points of
%% the intersection between a ball $\Ball{R/h}{\vx/h}$ of digital radius
%% $R/h$ and $\DigShape$ (we denote such quantity $\AreaC(Y,h)$ in
%% dimension 2):
%
\begin{Definition}
  %
  Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
  (or $\R^3$ for the 3D mean curvature estimator), \emph{digital curvature
  estimators} are defined for any point $\vx \in \R^2$ (or $\R^3$) as:
  %
  \vspace{-0.05cm}
  %
  \begin{align}
    \forall 0 < h < R,\quad
    &\CurvH{R}(Z,\vx,h) \EqDef \frac{3\pi}{2R}
    - \frac{3\AreaC(\Ball{R/h}{\vx/h} \cap
    {Z}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
    &\MeanCurvH{R}(Z,\vx,h) \EqDef \frac{8}{3R}
    - \frac{4\VolC(\Ball{R/h}{\vx/h} \cap
    Z, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
  \end{align}
  %
  where $\Ball{R/h}{\vx/h}$ is the ball of digital radius $R/h$ centered on
  digital point $(\vx/h) \in Z$.
  %
  % \AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
  % \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
  % \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
  % the number of digital points in the intersection between $\Body{\DSh}{h}$ and
  % the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
  % $h^d$.\todo[inline]{J: Hum... pas top...}
  %
  % Similarly, $\hat{\lambda}_1$
  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
  % matrix of the digital points in the intersection between $Z$ and the ball.
  %
\end{Definition}
%
\comJeremy{Such curvature estimators have multigrid convergence
  properties~\cite{DGCI2013}:} when the digital object becomes finer
and finer, \ie when the digitization step $h$ tends to zero, the
estimated quantities on $\Bd{\Body{\DSh}{h}}$ converges (theoretically
and experimentally) to the \txtblue{ associated one on $\Bd{\Shape}$
  in $O\left(h^{\frac{1}{3}}\right)$ for convex shapes with at least
  $C^3$-boundary and bounded curvature (setting $R\EqDef
  kh^\frac{1}{3}$ for some $k\in\R$).}
%
%Since our digital estimators are defined on
%digital shapes, in order to compare results with the exact curvature on
%Euclidean shape, we need to match points on boundary of the digital
%shape and points on the border of the Euclidean one.
%
%Setting $R = kh^\frac{1}{3}$ on convex shapes
%with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
%related to the maximal curvature of the shape, they have:
%%
%\begin{align}
%\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
%\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
%&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
%&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
%\end{align}
